Summary of models

### 2022-10-11 Rmd/Models.Rmd
apis and no apis

@@

@@

@@

@@

@@

>>>>

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
#plot
plots_fruitproportion_polli_no_apis <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=No_Apis_visit_rate, y=fruit_proportion) + 
  geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion_polli_no_apis[[1]],plots_fruitproportion_polli_no_apis[[2]],plots_fruitproportion_polli_no_apis[[3]],plots_fruitproportion_polli_no_apis[[4]],plots_fruitproportion_polli_no_apis[[5]],plots_fruitproportion_polli_no_apis[[6]],plots_fruitproportion_polli_no_apis[[7]],plots_fruitproportion_polli_no_apis[[8]],plots_fruitproportion_polli_no_apis[[9]],plots_fruitproportion_polli_no_apis[[10]],plots_fruitproportion_polli_no_apis[[11]],plots_fruitproportion_polli_no_apis[[12]], ncol=3, nrow=4)

\newpage
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

@@

\newpage
Data were 'prettified'. Consider using `terms="No_Apis_visit_rate [all]"` to get smooth plots.
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

Problemas C.libanotis 
Warning messages:
1: In vcov.merMod(object, use.hessian = use.hessian) :
  variance-covariance matrix computed from finite-difference Hessian is
not positive definite or contains NA values: falling back to var-cov estimated from RX
2: In vcov.merMod(object, correlation = correlation, sigm = sig) :
  variance-covariance matrix computed from finite-difference Hessian is
not positive definite or contains NA values: falling back to var-cov estimated from RX

@@

\newpage
Data were 'prettified'. Consider using `terms="Apis_visit_rate [all]"` to get smooth plots.
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

## Hymenoptera visitation rate without A.mellifera
```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_fruitproportion_hyme_no_apis <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=Hym_visit_sin_apis, y=fruit_proportion) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion_hyme_no_apis[[1]],plots_fruitproportion_hyme_no_apis[[2]],plots_fruitproportion_hyme_no_apis[[3]],plots_fruitproportion_hyme_no_apis[[4]],plots_fruitproportion_hyme_no_apis[[5]],plots_fruitproportion_hyme_no_apis[[6]],plots_fruitproportion_hyme_no_apis[[7]],plots_fruitproportion_hyme_no_apis[[8]],plots_fruitproportion_hyme_no_apis[[9]],plots_fruitproportion_hyme_no_apis[[10]],plots_fruitproportion_hyme_no_apis[[11]],plots_fruitproportion_hyme_no_apis[[12]], ncol=3, nrow=4)

Problemas H.calycinum: unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

@@

\newpage
Data were 'prettified'. Consider using `terms="Hym_visit_sin_apis [all]"` to get smooth plots
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
